A Generic and Efficient E-field Parallel Imaging Correlator for Next-Generation Radio Telescopes

### 2016-06-21 imaging_demo/ms.tex
Make few changes addressing referee comments
From 2add9d8 (mnras):
====================

In ms.tex,

(*) Make few changes addressing referee comments

\par\medskip
\noindent {\bf Temporal Fourier transform}
\par\medskip
\noindent This module is common to the MOFF and visibility-based imaging 
techniques. Time samples of electric fields measured by the antenna and 
digitized by the A/D converter is Fourier transformed to generate electric 
field spectra. This step can be parallelized across antennas as shown in 
Fig.~\ref{fig:f-engine}. The output is then fed to either MOFF or 
visibility-based imaging pipelines.

\begin{figure}
  \includegraphics[width=\columnwidth]{figure4}
  % \includegraphics[width=\columnwidth]{parallel_F_engine}
  % \includegraphics[width=\columnwidth]{parallel_F_engine.eps}
  \caption{Block diagram of a F-engine. The electric field data streams from
    antennas are Fourier transformed in parallel to generate electric field
    spectra.}
  \label{fig:f-engine}
\end{figure}

@@

In a companion paper to appear soon, we demonstrate a novel calibration 
technique (EPICal) which leverages the data products formed by direct imaging 
correlators to estimate antenna complex gains. This method correlates the antenna 
electric field signals with an image pixel from the output of the correlator in 
the feedback calibration fashion outlined in \citealt{mor11} (illustrated in 
Fig.~\ref{fig:MOFF-flowchart} by the arrow leading from the imager to the 
calibration block). Furthermore it allows for arbitrarily complex sky models, 
and following the MOFF algorithm places no restriction on array layout, and 
accounts for non-identical antenna beam patterns. Direction dependent calibration 
can be achieved by correlating antenna signals with output pixels in the 
direction of $N_\textrm{c}$ calibration sources, then fitting for a functional 
model of the sky. Since antennas are only correlated with calibrator pixels, the 
computational complexity scales as $\sim N_\textrm{a} N_\textrm{c}$.

>>>>

\par\medskip
\noindent {\bf Temporal Fourier transform}
\par\medskip
\noindent This module is common to the MOFF and visibility-based imaging 
techniques. Time samples of electric fields measured by the antenna and 
digitized by the A/D converter is Fourier transformed to generate electric 
field spectra. This step can be parallelized across antennas%  as shown in 
% Fig.~\ref{fig:f-engine}
. The output is then fed to either MOFF or 
visibility-based imaging pipelines.

% \begin{figure}
%   \includegraphics[width=\columnwidth]{figure4}
%   % \includegraphics[width=\columnwidth]{parallel_F_engine}
%   % \includegraphics[width=\columnwidth]{parallel_F_engine.eps}
%   \caption{Block diagram of a F-engine. The electric field data streams from
%     antennas are Fourier transformed in parallel to generate electric field
%     spectra.}
%   \label{fig:f-engine}
% \end{figure}

@@

In a companion paper \citep{bea16}, we demonstrate a novel calibration 
technique (EPICal) which leverages the data products formed by direct imaging 
correlators to estimate antenna complex gains. This method correlates the antenna 
electric field signals with an image pixel from the output of the correlator in 
the feedback calibration fashion outlined in \citealt{mor11} (illustrated in 
Fig.~\ref{fig:MOFF-flowchart} by the arrow leading from the imager to the 
calibration block). Furthermore it allows for arbitrarily complex sky models, 
and following the MOFF algorithm places no restriction on array layout, and 
accounts for non-identical antenna beam patterns. Direction dependent calibration 
can be achieved by correlating antenna signals with output pixels in the 
direction of $N_\textrm{c}$ calibration sources, then fitting for a functional 
model of the sky. Since antennas are only correlated with calibrator pixels, the 
computational complexity scales as $\sim N_\textrm{a} N_\textrm{c}$.
